\bf A Continuous-time Multicast \\Network Model

### 2018-05-09 paper/paper.tex
PPE results
writing more about out of sample stuff
compiled pdf

The HeEM ({\bf Hyper-edge event model)	has many component parts that need to be specified by the user (i.e., the selection of the event timing features ($\bm{y}$), the recipient selection features $(\bm{x}$), and the event time distribution ($g$)). Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification. For example, though theoretical considerations may inform the specification of features, subject-matter expertise is unlikely to inform the decision regarding the family of the event time distribution. Furthermore, since different distribution families (and model specifications more generally) may involve different size parameter spaces, any data-driven approach to model comparison must guard against over-fitting the data. In this section we present a general-purpose approach to evaluating a HeEM specification using out-of-sample prediction. We illustrate this approach by comparing alternative distributional families for the event timing component of the model.

@@

After running the experiment, we measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
	\begin{figure}[!b]
		\centering
		\includegraphics[width=0.33\textwidth]{plots_paper/outdegreenew-1.png}	
		\includegraphics[width=0.33\textwidth]{plots_paper/indegreenew-1.png}	
		\includegraphics[width=0.33\textwidth]{plots_paper/recipientsizenew-1.png}	
		\caption {PPE results}
		\label{figure:PPEresults}
	\end{figure}

>>>>

The HeEM ({\bf Hyper-edge event model})	has many component parts that need to be specified by the user (i.e., the selection of the event timing features ($\bm{y}$), the recipient selection features $(\bm{x}$), and the event time distribution ($g$)). Many of these components will be specified based on user expertise (e.g., regarding which features would drive recipient selection), but some decisions may require a data-driven approach to model specification. For example, though theoretical considerations may inform the specification of features, subject-matter expertise is unlikely to inform the decision regarding the family of the event time distribution. Furthermore, since different distribution families (and model specifications more generally) may involve different size parameter spaces, any data-driven approach to model comparison must guard against over-fitting the data. In this section we present a general-purpose approach to evaluating a HeEM specification using out-of-sample prediction. We illustrate this approach by comparing alternative distributional families for the event timing component of the model.

Good example article: \url{https://projecteuclid.org/download/pdfview_1/euclid.ba/1457383101}

@@

After running the experiment, we measure the predictive performance of two separate time distributions using 500 predicted samples, which are depicted in Figure \ref{figure:PPEresults}.
	\begin{figure}[!b]
		\centering
		\includegraphics[width=0.495\textwidth]{plots_paper/senderpredict-1.png}	
		\includegraphics[width=0.495\textwidth]{plots_paper/receiverpredict2-1.png}	
		\caption {PPE results}
		\label{figure:PPEresults}
	\end{figure}
